
# R SessionInfo

R version 3.6.1 (2019-07-05)
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows 10 x64 (build 18363)

Matrix products: default

locale:
[1] LC_COLLATE=German_Germany.1252  LC_CTYPE=German_Germany.1252   
[3] LC_MONETARY=German_Germany.1252 LC_NUMERIC=C                   
[5] LC_TIME=German_Germany.1252    

attached base packages:
[1] grid      stats     graphics  grDevices utils     datasets  methods  
[8] base     

other attached packages:
 [1] mediation_4.5.0   sandwich_2.5-1    mvtnorm_1.0-11    Matrix_1.2-17    
 [5] MASS_7.3-51.4     cowplot_1.0.0     fastDummies_1.5.0 gridExtra_2.3    
 [9] Zelig_5.1.6.1     survival_2.44-1.1 stargazer_5.2.2   gtools_3.8.1     
[13] mlogit_1.0-1      lmtest_0.9-37     zoo_1.8-6         Formula_1.2-3    
[17] forcats_0.4.0     stringr_1.4.0     dplyr_0.8.3       purrr_0.3.3      
[21] readr_1.3.1       tidyr_1.0.0       tibble_2.1.3      ggplot2_3.2.1    
[25] tidyverse_1.2.1   readstata13_0.9.2

loaded via a namespace (and not attached):
 [1] minqa_1.2.4         VGAM_1.1-1          colorspace_1.4-1   
 [4] rio_0.5.16          htmlTable_1.13.2    base64enc_0.1-3    
 [7] rstudioapi_0.10     MatrixModels_0.4-1  lubridate_1.7.4    
[10] xml2_1.2.2          splines_3.6.1       knitr_1.25         
[13] zeallot_0.1.0       jsonlite_1.6        nloptr_1.2.1       
[16] mcmc_0.9-6          broom_0.5.2         cluster_2.1.0      
[19] geepack_1.2-1       compiler_3.6.1      httr_1.4.1         
[22] backports_1.1.5     assertthat_0.2.1    lazyeval_0.2.2     
[25] survey_3.36         cli_1.1.0           acepack_1.4.1      
[28] htmltools_0.4.0     quantreg_5.51       tools_3.6.1        
[31] coda_0.19-3         gtable_0.3.0        glue_1.3.1         
[34] Rcpp_1.0.2          carData_3.0-2       cellranger_1.1.0   
[37] vctrs_0.2.0         Amelia_1.7.5        nlme_3.1-140       
[40] gbRd_0.4-11         xfun_0.10           openxlsx_4.1.0.1   
[43] lme4_1.1-21         rvest_0.3.4         lpSolve_5.6.13.3   
[46] lifecycle_0.1.0     statmod_1.4.32      scales_1.0.0       
[49] miscTools_0.6-24    hms_0.5.1           SparseM_1.77       
[52] RColorBrewer_1.1-2  curl_4.2            rpart_4.1-15       
[55] latticeExtra_0.6-28 stringi_1.4.3       checkmate_1.9.4    
[58] AER_1.2-7           boot_1.3-22         zip_2.0.4          
[61] bibtex_0.4.2        Rdpack_0.11-0       rlang_0.4.2        
[64] pkgconfig_2.0.3     lattice_0.20-38     htmlwidgets_1.5.1  
[67] labeling_0.3        tidyselect_0.2.5    magrittr_1.5       
[70] R6_2.4.0            generics_0.0.2      Hmisc_4.2-0        
[73] DBI_1.0.0           pillar_1.4.2        haven_2.1.1        
[76] foreign_0.8-71      withr_2.1.2         abind_1.4-5        
[79] nnet_7.3-12         modelr_0.1.5        crayon_1.3.4       
[82] car_3.0-3           maxLik_1.3-6        readxl_1.3.1       
[85] data.table_1.12.4   digest_0.6.21       MCMCpack_1.4-4     
[88] MatchIt_3.0.2       stats4_3.6.1        munsell_0.5.0      
[91] mitools_2.4  

# Load Data

```{r Load Data}
rm(list=ls())
source("auxiliary files/load_data.R")
```


# Figure 2
## The Swedish party system in the 2018 general election campaign

```{r Figure 2}
source("auxiliary files/figure2.R")
figure2
```

# Figure 3/ Figure 10 (Appendix)
## Condition Average Treatment Effects on Propensities to Vote for Other Parties

```{r Figure 3/ Figure 10 (Appendix)}

source("auxiliary files/figure3figure10.R")

```


# Figure 4
## Average causal treatment effect ofcoalition signals on perceived coalition likelihoods

```{r Figure 4}

source("auxiliary files/figure4.R")

```


# Figure 5/ Figure 13 (Appendix)
## Treatment Effect on Perceived Positions of Other Parties

```{r Figure 5/ Figure 13 (Appendix)}

source("auxiliary files/figure5figure13.R")

```


# Figure 6/ Figure 16(a) (Appendix)
## Average causal mediation effects (ACME) of treatments via likelihood of treatment coalition on propensitiesto vote by treatment coalition ratings/ Sensitivity analysis

```{r Figure 6/ Figure 16(a) (Appendix)}

source("auxiliary files/figure6figure16a.R")

```


# Figure 7/ Figure 17 (Appendix)/ Table 6 (Appendix)
## Effect of coalition ratings on expected propensities to vote by treatment and control status

```{r Figure 7/ Figure 17 (Appendix)/ Table 6 (Appendix)}

source("auxiliary files/figure7figure17table6.R")

```


# Table 4 (Appendix)
## Descriptive statistics

```{r Table 4 (Appendix)}

source("auxiliary files/table4.R")

```



# Table 5 (Appendix)
## Randomization Test

```{r Table 5 (Appendix)}

source("auxiliary files/table5.R")
summary(rand_test)

```


# Figure 8 (Appendix)/ Figure 9 (Appendix)
## Unconditional Treatment Effect on Propensities to Vote

```{r Figure 8 (Appendix)/ Figure 9 (Appendix)}

source("auxiliary files/figure8figure9.R")

```


# Figure 11 (Appendix)/ Figure 12 (Appendix)
## Conditional average treatment effects on propensities to vote for a stricter definition of low and high coalition evaluations


```{r Figure 11 (Appendix)/ Figure 12 (Appendix)}

source("auxiliary files/figure11figure12.R")

```


# Figure 14 (Appendix)/ Figure 16(b) (Appendix)
## Average causal mediation effects (ACME) of Treatment M-SD via M-SD coalition likelihood on propensi-ties to vote for centrist voters/ Sensitivity analysis

```{r Figure 14 (Appendix)/ Figure 16(b) (Appendix)}

source("auxiliary files/figure14figure16b.R")

```


# Figure 15 (Appendix)
## Average causal mediation effects (ACME) of Treatment SAP-MP via SAP-MP coalition likelihood onpropensities to vote for centrist voters

```{r Figure 15 (Appendix)}

source("auxiliary files/figure15.R")

```


# Figure 18
## Effect of coalition ratings on expected propensities to vote by treatment and control status (stacking)

```{r Figure 18}

source("auxiliary files/figure18.R")

```
